---
title: "Final_Project"
author: "Ayushi Singhal"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Read data from the main excel file
```{r}
library(readxl)
MoviesOnStreamingPlatforms <- read_excel("C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/MoviesOnStreamingPlatforms.xlsx", 
    sheet = "MoviesOnStreamingPlatforms")
```

## Read data from the additional netflix excel file
```{r warning=FALSE}
library(readxl)
netflix_titles <- read_excel("C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/netflix_titles.xlsx", 
    sheet = "netflix_titles")
```

## Read data from the additional amazon excel file
```{r}
library(readxl)
amazon_prime_titles <- read_excel("C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/amazon_prime_titles.xlsx", 
    sheet = "amazon_prime_titles")
```


## Read data from the additional Hulu excel file
```{r warning=FALSE}
library(readxl)
hulu_titles <- read_excel("C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/hulu_titles.xlsx", 
    sheet = "hulu_titles")
```

## Read data from the additional disney plus excel file
```{r}
library(readxl)
disney_plus_titles <- read_excel("C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/disney_plus_titles.xlsx",
    sheet = "disney_plus_titles")
```


```{r}
#Fetching the selected columns from the Netflix additional file and creating a subset of it to have the names of the columns. 
library(dplyr)
netflix_titles_subset<-netflix_titles[,c('Title','director','cast','country','duration','listed_in')]
colnames(netflix_titles_subset)<-c('Title','director_n','cast_n','country_n','duration_n','listed_in_n')

#Joining the additional Netflix file's data with the main file(Using the join on Title)
MoviesOnStreamingPlatforms_n<-MoviesOnStreamingPlatforms%>%
  left_join(netflix_titles_subset,by='Title')

#Picking up the unique data
MoviesOnStreamingPlatforms_n<-unique(MoviesOnStreamingPlatforms_n)
```


```{r}
#Fetching the selected columns from the Amazon's additional file and creating a subset of it to have the names of the columns. 
amazon_titles_subset<-amazon_prime_titles[,c('Title','director','cast','country','duration','listed_in')]
colnames(amazon_titles_subset)<-c('Title','director_a','cast_a','country_a','duration_a','listed_in_a')

#Joining the additional Amazon file's data with the main file(Using the join on Title)
MoviesOnStreamingPlatforms_na<-MoviesOnStreamingPlatforms_n%>%
  left_join(amazon_titles_subset,by="Title")

#Picking up the unique data
MoviesOnStreamingPlatforms_na<-unique(MoviesOnStreamingPlatforms_na)
```


```{r}
#Fetching the selected columns from the Hulu's additional file and creating a subset of it to have the names of the columns. 
hulu_titles_subset<-hulu_titles[,c('Title','director','cast','country','duration','listed_in')]
colnames(hulu_titles_subset)<-c('Title','director_h','cast_h','country_h','duration_h','listed_in_h')

#Joining the additional Hulu's file's data with the main file(Using the join on Title)
MoviesOnStreamingPlatforms_nah<-MoviesOnStreamingPlatforms_na%>%
  left_join(hulu_titles_subset,by="Title")

#Picking up the unique data
MoviesOnStreamingPlatforms_nah<-unique(MoviesOnStreamingPlatforms_nah)
```

```{r}
#Fetching the selected columns from the Disney's additional file and creating a subset of it to have the names of the columns. 
disney_titles_subset<-disney_plus_titles[,c('Title','director','cast','country','duration','listed_in')]
colnames(disney_titles_subset)<-c('Title','director_d','cast_d','country_d','duration_d','listed_in_d')

#Joining the additional Disney's file's data with the main file(Using the join on Title)
MoviesOnStreamingPlatforms_nahd<-MoviesOnStreamingPlatforms_nah%>%
  left_join(disney_titles_subset,by="Title")

#Picking up the unique data
MoviesOnStreamingPlatforms_nahd<-unique(MoviesOnStreamingPlatforms_nahd)

MoviesOnStreamingPlatforms_nahd
```



```{r}
#Merging the additional fetched columns(Director,Cast,Country,Duration,Listed_In) into one of the type column.
MoviesOnStreamingPlatforms_nahd%>%
  mutate(director_n=ifelse(`Prime Video`==1,director_a,ifelse(Hulu==1,director_h,ifelse(`Disney+`==1,director_d,director_n))))

MoviesOnStreamingPlatforms_nahd%>%
  mutate(cast_n=ifelse(`Prime Video`==1,cast_a,ifelse(Hulu==1,cast_h,ifelse(`Disney+`==1,cast_d,cast_n))))

MoviesOnStreamingPlatforms_nahd%>%
  mutate(country_n=ifelse(`Prime Video`==1,country_a,ifelse(Hulu==1,country_h,ifelse(`Disney+`==1,country_d,country_n))))

MoviesOnStreamingPlatforms_nahd%>%
  mutate(duration_n=ifelse(`Prime Video`==1,duration_a,ifelse(Hulu==1,duration_h,ifelse(`Disney+`==1,duration_d,duration_n))))

MoviesOnStreamingPlatforms_nahd%>%
  mutate(duration_n=ifelse(`Prime Video`==1,listed_in_a,ifelse(Hulu==1,listed_in_h,ifelse(`Disney+`==1,listed_in_d,listed_in_n))))

#Drop the additional junk columns
##Collects the names of the columns to be dropped
drops <- c("director_a","director_h","director_d","cast_a","cast_h","cast_d","country_a","country_h","country_d","duration_a","duration_h","duration_d","listed_in_a","listed_in_h","listed_in_d")
##Dropping off the columns
MoviesOnStreamingPlatforms_nahd<-MoviesOnStreamingPlatforms_nahd[, !(names(MoviesOnStreamingPlatforms_nahd) %in% drops)]

#Renaming the new columns
MoviesOnStreamingPlatforms_nahd<-MoviesOnStreamingPlatforms_nahd %>% 
   rename(
     director = director_n,
     cast= cast_n,
     country=country_n,
     duration=duration_n,
     genre=listed_in_n
     )

#Replacing the commas present in the columns by semi-colons for readable data generation in excel file.
library(tidyverse)
MoviesOnStreamingPlatforms_nahd <- MoviesOnStreamingPlatforms_nahd %>%
    map_df(str_replace, pattern = ",", replacement = ";")




```
```{r}
#Data Cleaning
##Removing rows with no ratings(NA), titles starting with decimal numbers,removal of hash from titles and removing min from duration
MoviesOnStreamingPlatforms_nahd<-MoviesOnStreamingPlatforms_nahd%>%
  filter(!is.na(`Rotten Tomatoes`))%>%
  filter(!grepl("^[0]", Title))%>%
  mutate(Title = gsub("#", "", Title),
         duration=gsub("min", "", duration))

```

```{r}
# Writing data in an excel file

write.csv(MoviesOnStreamingPlatforms_nahd,"C:/Users/ayush/OneDrive/Desktop/College/Quarter 1/OPS 801 - Data Analysis/Project/Data File/MoviesOnStreamingPlatform_updated", row.names=FALSE)
```


# Statistical Analysis

```{r}
#Splitting the rating's columns
library(tidyr)

MoviesOnStreamingPlatforms_nahd <- MoviesOnStreamingPlatforms_nahd %>% separate(`Rotten Tomatoes`, sep = "/", into = c('rating','out_of'), remove = FALSE)

#Converting the flagging columns of all the platforms to numeric from string
MoviesOnStreamingPlatforms_nahd$platform_count<-as.numeric(MoviesOnStreamingPlatforms_nahd$Netflix)+
  as.numeric(MoviesOnStreamingPlatforms_nahd$`Prime Video`)+
  as.numeric(MoviesOnStreamingPlatforms_nahd$Hulu)+
  as.numeric(MoviesOnStreamingPlatforms_nahd$`Disney+`)

#Tabulation for platform count 
table(MoviesOnStreamingPlatforms_nahd$platform_count)
str(MoviesOnStreamingPlatforms_nahd)

#Adding a new column 'Platform' converted from the flagging columns to indicate the movies are from which platform.
MoviesOnStreamingPlatforms_nahd<-MoviesOnStreamingPlatforms_nahd%>%
  mutate(platform=ifelse(Netflix=='1' & platform_count==1,'Netflix',
                         ifelse(`Prime Video`==1 & platform_count==1,'Prime',
                                ifelse(Hulu==1 & platform_count==1,'Hulu',
                                       ifelse(`Disney+`==1 & platform_count==1,'Disney','multiple_platforms')))))
MoviesOnStreamingPlatforms_nahd$rating<-as.numeric(MoviesOnStreamingPlatforms_nahd$rating)
summary(MoviesOnStreamingPlatforms_nahd)

#Tabulation for platform-- States the number of entries for specific platforms(Frequency)
table(MoviesOnStreamingPlatforms_nahd$platform)

#Gives the Average of the ratings against the Number of Movies on the basis of platform
MoviesOnStreamingPlatforms_nahd%>%
  group_by(platform)%>%
  summarise(movies=n(),
            avg_rating=mean(rating,na.rm=T))

#Gives the Average of the ratings against the Number of Movies on the basis of age
MoviesOnStreamingPlatforms_nahd%>%
  group_by(Age)%>%
  summarise(movies=n(),
            avg_rating=mean(rating,na.rm=T))

#Gives the Average of the Ratings & the number of movies on the basis of age and platform
x<-MoviesOnStreamingPlatforms_nahd%>%
  group_by(Age,platform)%>%
  summarise(movies=n(),
            avg_rating=mean(rating,na.rm=T))
x

table(MoviesOnStreamingPlatforms_nahd$Age,MoviesOnStreamingPlatforms_nahd$platform)

```

## Chi-Square Testing

$H_0$: Age Ratings of platforms are independent.

$H_a$: Age Ratings of platforms are not independent.
```{r}
#Filters the data with age having 'NA' and the titles with multiple platforms. 
x<-MoviesOnStreamingPlatforms_nahd%>%
  filter(!is.na(Age) & platform!='multiple_platforms')

#Chi Square test on Age & Platform
chisq.test(table(x$platform,x$Age))

#Tabulation of Age and platform
table(x$platform,x$Age)

#Calculating probability
y<-x%>%
  group_by(Age)%>%
  summarise(totals=n())
y$probability<-y$totals/sum(y$totals)

#Checking total number of titles in each platform
z<-x%>%
  group_by(platform)%>%
  summarise(totals=n())


x<-MoviesOnStreamingPlatforms_nahd%>%
  filter(platform!='multiple_platforms')
x$platform=as.factor(x$platform)

#Box-plot of Platforms vs Ratings
boxplot(rating ~ platform, xlab='Platform', ylab='Rating', data=x)

#Bartlett's test to check if k samples have equal variances
bartlett.test(rating ~ platform, data=x)
```



$H_0$: Movie Ratings and Platform are independent.
$H_a$: Movie Ratings and Platform are not independent.
```{r}
#Anova testing 
anova=aov(x$rating~x$platform)
summary(anova)

#Tukey's testing
TukeyHSD(anova, conf.level=.95)

```



